### 2025-11-21 about/vita.tex
new paper and updated 242 tut2
tut10 and other updates

\sectheader{Papers}

\begingroup\frenchspacing
\papercount=8
\pubbegin P
\papitem (with Tsun-Ming Cheung and Luc Devroye)
A note on plane trees with decreasing labels.
To appear in {\sl Online Journal of Analytic Combinatorics}.
[arXiv:2502.14596]
\papitem An uncertainty principle for M\"obius inversion on posets.
To appear in {\sl Contributions to Discrete Mathematics}.
[arXiv:2302.02466]
\papitem (with Jonah Saks)
On the homology of several number-theoretic set families.
{\sl Enumerative Combinatorics and Applications}\/ {\bf 4},2 (2024), \#S2R12, 11~pp.
[arXiv:2206.12535]
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions.
{\sl Australasian Journal of Combinatorics}\/ {\bf 84},3 (2022), 357--374.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
{\sl Combinatorics, Probability and Computing}\/ {\bf 32},1 (2023), 68--90.
[arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science}\/ {\bf 24},1 (2022), \#7, 16~pp.
[arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms}\/ {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory}\/ {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\begingroup\frenchspacing\parindent=10pt
\thing (with Hamed Hatami)
Block structure in boolean matrices of small factorization norm.
{\sl arXiv:2507.00872} (2025), 14~pp.
\smallskip
\thing (with Hamed Hatami)
Block complexity and idempotent Schur multipliers.
{\sl arXiv:2506.21752} (2025), 17~pp.
\smallskip
\thing
On an entropic analogue of additive energy.
{\sl arXiv:2406.18798} (2025), 19~pp.
\endgroup

>>>>

\sectheader{Papers {\rm(in reverse order of acceptance, not necessarily appearance)}}

\begingroup\frenchspacing
\papercount=9
\pubbegin P
\papitem (with Hamed Hatami)
Block complexity and idempotent Schur multipliers.
To appear in {\sl International Mathematics Research Notices}.
[arXiv:2506.21752]
\papitem (with Tsun-Ming Cheung and Luc Devroye)
A note on plane trees with decreasing labels.
{\sl Online Journal of Analytic Combinatorics}\/ {\bf 20} (2025), \#2, 9~pp.
[arXiv:2502.14596]
\papitem An uncertainty principle for M\"obius inversion on posets.
To appear in {\sl Contributions to Discrete Mathematics}.
[arXiv:2302.02466]
\papitem (with Jonah Saks)
On the homology of several number-theoretic set families.
{\sl Enumerative Combinatorics and Applications}\/ {\bf 4},2 (2024), \#S2R12, 11~pp.
[arXiv:2206.12535]
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions.
{\sl Australasian Journal of Combinatorics}\/ {\bf 84},3 (2022), 357--374.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
{\sl Combinatorics, Probability and Computing}\/ {\bf 32},1 (2023), 68--90.
[arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science}\/ {\bf 24},1 (2022), \#7, 16~pp.
[arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms}\/ {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory}\/ {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\begingroup\frenchspacing\parindent=10pt
\thing (with Hamed Hatami)
Block structure in boolean matrices of small factorization norm.
{\sl arXiv:2507.00872} (2025), 14~pp.
\smallskip
\thing
On an entropic analogue of additive energy.
{\sl arXiv:2406.18798} (2025), 19~pp.
\endgroup
